---
title: "p8105_hw6_fs2757"
author: "FEI SUN"
date: "2021/12/2"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
set.seed(1)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```
# Problem 1
```{r}
birthweight_raw = 
  read_csv("data/birthweight.csv") %>% 
  janitor::clean_names()%>% 
  mutate(
    babysex = case_when(babysex == "1" ~ "male",
                        babysex == "2" ~ "female"),
    frace = case_when(frace == "1" ~ "White",
                      frace == "2" ~ "Black",
                      frace == "3" ~ "Asian",
                      frace == "4" ~ "Puerto Rican", 
                      frace == "8" ~ "Other",
                      frace == "9" ~ "Unknown"),
    malform = case_when(malform == "0" ~ "absent",
                        malform == "1" ~ "present"),
    mrace = case_when(mrace == "1" ~ "White",
                      mrace == "2" ~ "Black",
                      mrace == "3" ~ "Asian",
                      mrace == "4" ~ "Puerto Rican",
                      mrace == "8" ~ "Other"),
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace))

skimr::skim(birthweight_raw)

```

There are no missing value in the dataset. Also I convert the numeric variable to the factor.

```{r}
model1 = lm(bwt ~gaweeks + babysex + mheight + ppwt + wtgain + parity + smoken + bhead + mrace + frace + malform, data = birthweight_raw)
summary(model1)
broom::tidy(model1)

birthweight_raw %>% 
  modelr::add_residuals(model1) %>% 
  modelr::add_predictions(model1) %>% 
  ggplot(aes(x = pred, y = resid,color=babysex))+
  geom_point(alpha = 0.3)+
  geom_smooth(color = "green",method = "lm", se = F)+
  facet_grid(. ~ babysex)+
  labs(
    x = "Fitted Value",
    y = "Residuals",
    title = "Plot of Residuals against Fitted Value"
  )

```

About model 1, I will using almost all clinically relevant variables as predictors(X) based on current literature and removed all non-significant predictors. From the plot, it shows that the residuals are relatively evenly distributed around y = 0 and it satisfies the linearity assumption.

```{r}
model2 = lm(bwt ~blength + gaweeks, data = birthweight_raw)
summary(model2)
broom::tidy(model2)

```



```{r}
model3 = lm(bwt ~bhead + blength + babysex + 
              bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight_raw)
summary(model3)
broom::tidy(model3)

```

```{r, message = FALSE, warning = FALSE}
cv_df =
  crossv_mc(birthweight_raw, 100) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))%>%
  mutate(
    model_1  = map(train, ~lm(bwt ~babysex + bhead + blength + delwt + fincome, data = .x)),
    model_2  = map(train, ~lm(bwt ~blength + gaweeks, data = .x)),
    model_3  = map(train, ~lm(bwt ~bhead + blength + babysex + 
              bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex,
              data = .x))) %>% 
  mutate(rmse_model1 = 
        map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
        rmse_model2 = 
        map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
        rmse_model3 =
        map2_dbl(model_3, test, ~rmse(model = .x, data = .y)))
cv_df
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
   labs(
        title = "RMSE AND MODELS",
        x = "Model",
        y = "Rmse"
      )

```

From the plot, the model 2 has the highest prediction error distribution and the model 1 has the lowest prediction error distribution

# Problem 2
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df 
```

```{r}
bootstrap_r =
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm( tmax ~ tmin , data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(.id, results) %>% 
  unnest(results)

bootstrap_r

bootstrap_r %>% 
ggplot(aes(x = r.squared)) + 
  geom_density() +
   labs(
      x = "R squared values",
      y = "Density",
      title = "Distribution of R Squared Estimates")

bootstrap_r%>% 
  summarize(
    CI_lower = quantile(r.squared, 0.025),
    CI_upper = quantile(r.squared, 0.975)
  ) %>% 
  knitr::kable()

```
The plot shows that the R squared estimates appear to be normally distributed with a mean with 0.911. The 95% confidence interval for r squared is (0.8932225, 0.9271586).


```{r}
bootstrap_log =
  weather_df %>% 
  modelr::bootstrap(n = 5000)%>% 
  mutate(
    models = map(strap, ~lm( tmax ~ tmin , data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(.id, results) %>% 
  unnest(results)%>% 
  select(.id, term, estimate) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>% 
  mutate(
    log = log(`(Intercept)` * tmin)
  ) 
bootstrap_log

bootstrap_log %>% 
ggplot(aes(x = log)) + 
  geom_density() +
   labs(
      x = "Log values",
      y = "Density",
      title = "Distribution of log valu")

bootstrap_log%>% 
  summarize(
    CI_lower = quantile(log, 0.025),
    CI_upper = quantile(log, 0.975)
  ) %>% 
  knitr::kable()
```
The plot shows that the log estimates appear to be normally distributed with a mean with 2.013 The 95% confidence interval for r squared is (1.964318, 2.05832).
